Reformulating phylogenetic mixed models to improve flexibility and speed

### 2018-09-18 main.tex
pushing ms

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/ssplot.pdf}
  \caption{\bmb{caption ??}}
\label{ssplot}
\end{figure}
\end{center}

@@

@@

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./csplot.pdf}
  \caption{\bmb{caption??}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
\includegraphics[scale=0.8,page=2]{./csplot.pdf}
\caption{\bmb{caption??}}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/ssplot.pdf}
  \caption{Old}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./git_push/plot.pdf}
  \caption{New}
\label{ssplot}
\end{figure}
\end{center}

@@

\begin{itemize}
\item{full model provides good estimates (except for correlation)}
\item{reduced models try to fit with whatever parameters they have available (over-estimates the simulation parameters)}
\item{no slope vs slope}
\item{no correlation vs correlation}
\item{as size/data/number of species increase, the parameter estimates gets better}
\item{single site models are fast}
\item{estimates gets closer to simulation parameter as number of species increase}
\item{lme4/tmb are fast, everything else is slow for multiple sites}
\end{itemize}

@@

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=1]{./csplot.pdf}
  \caption{old}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h]
  \includegraphics[scale=0.8,page=2]{./git_push/plot.pdf}
  \caption{new}
\end{figure}
\end{center}

% \begin{center}
% \begin{figure}[h]
% \includegraphics[scale=0.8,page=2]{./csplot.pdf}
% \caption{\bmb{caption??}}
% \end{figure}
% \end{center}
